New orbits for irregular satellites based on thousands of new observations and predictions of stellar occultations up to 2020

### 2016-04-28 Irregular-occ/Irregular-occ.tex
.

\begin{table}
\caption{\label{Tab: satellite-diameter} Estimated diameter of the satellites and correspondent apparent diameter}
\begin{center}
\begin{tabular}{lccc}
\hline  \hline
\multicolumn{4}{c}{Diameter of the satellites} \tabularnewline
Satellite  & mas$^ {a}$  & km & Ref. \tabularnewline
\hline
Ananke & 8 & 29 & 1 \tabularnewline
Carme & 13 & 46 & 1 \tabularnewline
Elara & 24 & 86 & 1 \tabularnewline
Himalia & 41 & $(150\times120) \pm 20^{b}$ & 2 \tabularnewline
Leda & 5 & 20 & 1 \tabularnewline
Lysithea & 10 & 36 & 1 \tabularnewline
Pasiphae & 17 & 62 & 1 \tabularnewline
Sinope & 10 & 37 & 1 \tabularnewline
\hdashline
Phoebe & 32 & $212 \pm 1.4^{b}$ & 3 \tabularnewline
%\hdashline
%Nereid & 15 & $340 \pm 50^{c}$ & 4 \tabularnewline
%Triton & 124 & $2707 \pm 2.0^{c}$ & 5 \tabularnewline
\hline
\end{tabular}
\end{center}
References: (1) \cite{Rettig2001}; (2) \cite{Porco2003}; (3) \cite{Thomas2010}; (4) \cite{Thomas1991}; (5) \cite{Thomas2000}.\\
$^{a}${Using a mean distance from Jupiter of 5 AU, from Saturn of 9 AU and from Neptune of 30 AU.}
$^{b}${From Cassini observations.}
$^{c}${From Voyager-2 observations.}
\par
\end{table}

@@

\begin{table}
\caption{\label{Tab: satellite-occultation} Number of stellar occultations for each satellite from January, 2016 up to December, 2020.}
\begin{centering}
\begin{tabular}{lcccccc}
\hline  \hline
%\multicolumn{4}{c}{Diameter of the satellites} \tabularnewline
Satellite  & 2016 & 2017 & 2018 & 2019 & 2020 & Total \tabularnewline
\hline
Ananke & 12 & 16 & 49 & 359 & 187 & 623 \tabularnewline
Carme & 20 & 14 & 30 & 369 & 220 & 653 \tabularnewline
Elara & 14 & 16 & 33 & 305 & 193 & 561 \tabularnewline
Himalia & 15 & 12 & 54 & 257 & 230 & 568 \tabularnewline
Leda & 8 & 24 & 38 & 362 & 208 & 640 \tabularnewline
Lysithea & 16 & 11 & 35 & 330 & 212 & 604 \tabularnewline
Pasiphae & 20 & 19 & 44 & 362 & 206 & 651 \tabularnewline
Sinope & 15 & 21 & 34 & 356 & 256 & 682 \tabularnewline
\hdashline
Phoebe & 32 & 98 & 238 & 79 & 13 & 460 \tabularnewline
%\hdashline
%Nereid & 11$^{a}$ & 1 & 1 & 0 & 0 & 13 \tabularnewline
%Triton & -- & 1 & 1 & 0 & 0 & 2 \tabularnewline
\hline
\end{tabular}
\par \end{centering}
$^{a}$ {Using the WFI catalogue as explained in Sec. \ref{Sec: predictions}}.
\end{table}

@@

\cite{GomesJunior2015} also observed Sycorax (satellite of Uranus) and Nereid (satellites of Neptune). Sycorax had a few observations on 9 nights in two years which did not cover one orbital period. For Nereid, the observations covered many orbital periods, but due to Nereid's large orbital eccentricity there are no observations near the pericenter.

>>>>

\begin{table}
\caption{\label{Tab: satellite-diameter} Estimated diameter of the satellites and correspondent apparent diameter}
\begin{center}
\begin{tabular}{lccc}
\hline  \hline
\multicolumn{4}{c}{Diameter of the satellites} \tabularnewline
Satellite  & mas$^ {a}$  & km & Ref. \tabularnewline
\hline
Ananke & 8 & 29 & 1 \tabularnewline
Carme & 13 & 46 & 1 \tabularnewline
Elara & 24 & 86 & 1 \tabularnewline
Himalia & 41 & $(150\times120) \pm 20^{b}$ & 2 \tabularnewline
Leda & 5 & 20 & 1 \tabularnewline
Lysithea & 10 & 36 & 1 \tabularnewline
Pasiphae & 17 & 62 & 1 \tabularnewline
Sinope & 10 & 37 & 1 \tabularnewline
\hdashline
Phoebe & 32 & $212 \pm 1.4^{b}$ & 3 \tabularnewline
%\hdashline
%Nereid & 15 & $340 \pm 50^{c}$ & 4 \tabularnewline
%Triton & 124 & $2707 \pm 2.0^{c}$ & 5 \tabularnewline
\hline
\end{tabular}
\end{center}
References: (1) \cite{Rettig2001}; (2) \cite{Porco2003}; (3) \cite{Thomas2010}..\\
$^{a}${Using a mean distance from Jupiter of 5 AU, from Saturn of 9 AU and from Neptune of 30 AU.}
$^{b}${From Cassini observations.}
\par
\end{table}

@@

\begin{table}
\caption{\label{Tab: satellite-occultation} Number of stellar occultations for each satellite from January, 2016 up to December, 2020.}
\begin{centering}
\begin{tabular}{lcccccc}
\hline  \hline
%\multicolumn{4}{c}{Diameter of the satellites} \tabularnewline
Satellite  & 2016 & 2017 & 2018 & 2019 & 2020 & Total \tabularnewline
\hline
Ananke & 12 & 16 & 49 & 359 & 187 & 623 \tabularnewline
Carme & 20 & 14 & 30 & 369 & 220 & 653 \tabularnewline
Elara & 14 & 16 & 33 & 305 & 193 & 561 \tabularnewline
Himalia & 15 & 12 & 54 & 257 & 230 & 568 \tabularnewline
Leda & 8 & 24 & 38 & 362 & 208 & 640 \tabularnewline
Lysithea & 16 & 11 & 35 & 330 & 212 & 604 \tabularnewline
Pasiphae & 20 & 19 & 44 & 362 & 206 & 651 \tabularnewline
Sinope & 15 & 21 & 34 & 356 & 256 & 682 \tabularnewline
\hdashline
Phoebe & 32 & 98 & 238 & 79 & 13 & 460 \tabularnewline
%\hdashline
%Nereid & 11$^{a}$ & 1 & 1 & 0 & 0 & 13 \tabularnewline
%Triton & -- & 1 & 1 & 0 & 0 & 2 \tabularnewline
\hline
\end{tabular}
\par \end{centering}
\end{table}

@@

\cite{GomesJunior2015} also observed Sycorax (satellite of Uranus) and Nereid (satellite of Neptune). Sycorax had a few observations on 9 nights in two years which did not cover one orbital period. For Nereid, the observations covered many orbital periods, but due to Nereid's large orbital eccentricity there are no observations near the pericenter.
